Examining a Quarter Century of Publishing Trends in Social Work Research: A Data Science Perspective

### 2015-04-02 dataCleaning.Rmd
Additional cleaning and organization. All functional.

---
title: "Examining a Quarter Century of Publishing Trends in Social Work: A Data Science Perspective"
author: 
output: pdf_document
---

@@

```{r appendData, comment=NA, echo=FALSE, eval=FALSE}
appendData.f()

append.articles <- length(which(full.df$attributes == "article"))
append.journals <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())
```

```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE, eval=FALSE}
shortArticles.f()
```

```{r titleMatching, echo=FALSE, eval=FALSE}
titleMatching.f()

@@

journals.titleMatching <- filter(full.df, attributes == "journal") %>%
        summarise(Unique = n_distinct(record))
```

```{r otherDocuments, echo=FALSE, eval=FALSE}
otherDocuments.f()
articles.otherDocuments <- length(which(full.df$attributes == "article"))
journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r final, comment=NA, echo=FALSE, eval=FALSE}
fewArticles.f()
articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r finalList, comment=NA, echo=FALSE, eval=FALSE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r nsfPlot, eval=FALSE}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
     ylab("Doctoral degrees") +
     xlab("Year") +
     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
           title = element_text(size = 10)) +
     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

```{r eval=FALSE}
colnames(n.journals.year) <- c("years", "journals")
n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)

@@

scholarly.df <- mutate(scholarly.df, years = as.numeric(years)) %>%
    rename(article.count = year.count, journal.count = year.count, program.growth = growth) 
scholarly.df$gade <- rep(NA, nrow(scholarly.df))  
scholarly.df$gade[15] <- 72
scholarly.df$gade[27] <- 86

#write.csv(scholarly.df, file = "scholarship.csv")
```

```{r eval=FALSE}
save.image(file = "socialWorkHistory.Rdata")
```

@@

```{r message=FALSE, warning=FALSE, eval=FALSE}
cor.data <- select(final.list, first, last, n) %>%
            mutate(no.years = as.numeric(last) - as.numeric(first))

ggplot(cor.data, aes(x = no.years, y = n)) + 
            geom_point(shape = 1) + 
            geom_smooth() + 
            xlab("Years") + 
            ylab("Number of articles")
```

>>>>

---
title: "Examining a Quarter Century of Publishing Trends in Social Work Research: A Data Science Perspective"
author: 
output: pdf_document
---

@@

```{r dataCleaning, comment=NA, echo=FALSE, eval=FALSE}
appendData.f()
shortArticles.f()
titleMatching.f()
otherDocuments.f()
fewArticles.f()
save.image(file = "socialWorkHistory.Rdata")
```

```{r eval=TRUE}
append.articles <- length(which(full.df$attributes == "article"))
append.journals <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())

@@

journals.titleMatching <- filter(full.df, attributes == "journal") %>%
        summarise(Unique = n_distinct(record))

articles.otherDocuments <- length(which(full.df$attributes == "article"))
journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

```{r finalList, comment=NA, echo=FALSE, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r nsfPlot, eval=TRUE}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
     ylab("Doctoral degrees") +
     xlab("Year") +
     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
           title = element_text(size = 10)) +
     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

```{r eval=TRUE}
colnames(n.journals.year) <- c("years", "journals")
n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)

@@

scholarly.df <- mutate(scholarly.df, years = as.numeric(years)) %>%
    rename(article.count = year.count, journal.count = year.count, program.growth = growth) 
scholarly.df$gade <- rep(NA, nrow(scholarly.df))  
scholarly.df$gade[15] <- 72
scholarly.df$gade[27] <- 86
```

@@
